Event History Analysis for psychological time-to-event data: A tutorial in R with examples in Bayesian and frequentist workflows

### 2024-10-27 manuscript/manuscript.Rmd
add and delete REFs

For a comprehensive background context to event history analysis, we recommend several excellent textbooks [@singerAppliedLongitudinalData2003]. Likewise, for general introduction to understanding regression equations, we recommend several introductory level textbooks (REFs). Our focus here is not on providing a detailed account of the underlying regression equations, since this topics has been comprehensively covered many times before. Instead, we want to provide an intuition to how event history analysis works in general as well as in the context of experimental psychology. As such, we only supply regression equations in the supplementary material (part D) and then refer to them in the text whenever relevant.

@@

Based on previous work [@panisHowCanWe2020; @panisNeuropsychologicalEvidenceTemporal2017; @panisStudyingDynamicsVisual2020; @panisTimecourseContingenciesPerceptual2009; @panisWhenDoesInhibition2022] we expect nonlinear effects of trial number on the hazard of response occurrence. We thus relax all three assumptions in model 4. We add a squared term for the continuous predictor centered trial number -- I(trial_c^2) -- and include interaction terms.

>>>>

For a comprehensive background context to event history analysis, we recommend several excellent textbooks [@singerAppliedLongitudinalData2003; @allisonSurvivalAnalysisUsing2010]. Likewise, for general introduction to understanding regression equations, we recommend several introductory level textbooks (REFs). Our focus here is not on providing a detailed account of the underlying regression equations, since this topics has been comprehensively covered many times before. Instead, we want to provide an intuition to how event history analysis works in general as well as in the context of experimental psychology. As such, we only supply regression equations in the supplementary material (part D) and then refer to them in the text whenever relevant.

@@

Based on previous work [e.g., @panisHowCanWe2020] we expect nonlinear effects of trial number on the hazard of response occurrence. We thus relax all three assumptions in model 4. We add a squared term for the continuous predictor centered trial number -- I(trial_c^2) -- and include interaction terms. For example, how the effect of congruent primes changes across time bins within a trial might change across the trials within an experiment.

### 2024-10-27 manuscript/manuscript.tex
add and delete REFs

For a comprehensive background context to event history analysis, we recommend several excellent textbooks (Singer \& Willett, 2003). Likewise, for general introduction to understanding regression equations, we recommend several introductory level textbooks (REFs). Our focus here is not on providing a detailed account of the underlying regression equations, since this topics has been comprehensively covered many times before. Instead, we want to provide an intuition to how event history analysis works in general as well as in the context of experimental psychology. As such, we only supply regression equations in the supplementary material (part D) and then refer to them in the text whenever relevant.

@@

Based on previous work (Panis, 2020; Panis, Moran, et al., 2020; Panis \& Schmidt, 2022; Panis et al., 2017; Panis \& Wagemans, 2009) we expect nonlinear effects of trial number on the hazard of response occurrence. We thus relax all three assumptions in model 4. We add a squared term for the continuous predictor centered trial number -- I(trial\_c\^{}2) -- and include interaction terms.

>>>>

For a comprehensive background context to event history analysis, we recommend several excellent textbooks (Allison, 2010; Singer \& Willett, 2003). Likewise, for general introduction to understanding regression equations, we recommend several introductory level textbooks (REFs). Our focus here is not on providing a detailed account of the underlying regression equations, since this topics has been comprehensively covered many times before. Instead, we want to provide an intuition to how event history analysis works in general as well as in the context of experimental psychology. As such, we only supply regression equations in the supplementary material (part D) and then refer to them in the text whenever relevant.

@@

Based on previous work (e.g., Panis, 2020) we expect nonlinear effects of trial number on the hazard of response occurrence. We thus relax all three assumptions in model 4. We add a squared term for the continuous predictor centered trial number -- I(trial\_c\^{}2) -- and include interaction terms. For example, how the effect of congruent primes changes across time bins within a trial might change across the trials within an experiment.
